Extreme Value Chapter

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
MSE figure

@@

>>>>

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests),
         theta_diff= log_St_hat2 - theta) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            MSE = mean(theta_diff)^2,
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = MSE, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "MSE", title = "GLM Lomax") +
  theme_bw()

@@

# Figure 5
Bias correction

```{r}
